---
title: "Problems from crumplab.com"
author: "Ivar Hereide Mannsåker"
date: "2022-11-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Easy Problems

### Problem 3

Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

```{r}
One2Hundred <- c()
for (i in 1:100){
One2Hundred[i] <- i
}
One2seq <- seq(1,100)

print(One2Hundred)
print(One2seq)
```

### Problem 4

Find the sum of all the integer numbers from 1 to 100

With sum() function

```{r}
Summate <- sum(One2Hundred)
print(Summate)
```

With a loop

```{r}
SummateLoop <- 0L
for (i in 1:100) {
SummateLoop = SummateLoop + i
}

print(SummateLoop)
```

### Problem 5

Write a function to find the sum of all integers between any two values.

```{r}
SumAnyInterval <- function(IntStart,IntEnd){
  n <- 0
  for (i in IntStart:IntEnd){
    n = n+i
  }
  return(n)
}
```

Call the function:

```{r}
SumAnyInterval(5,200)
```

### Problem 6

List all of the odd numbers from 1 to 100.

Through the seq function:

```{r}
seq(1,100,by=2)
```

Through the use of mod and for loop

```{r}
Odds = c()
for (i in 1:100) {
  if (i%%2) {
    Odds = c(Odds,i)
  }
}
print(Odds)
```

### Problem 7
List all of the prime numbers from 1 to 1000.

```{r}
Primes <- c(2)
factors <- c(2)
for (i in seq(3,1000,by=2)){
  if (i%%factors){
    Primes <- c(Primes,i)
  }
  factors <- c(factors,i)
}
print(Primes)
```





### Problem 8
Generate 100 random numbers

```{r}
runif(100)
```


### Problem 9
Generate 100 random numbers within a specific range
```{r}
runif(100,2,5)
```


### Problem 10

