---
title: "Problems from crumplab.com"
author: "Ivar Hereide Mannsåker"
date: "2022-11-01"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Easy Problems

### Problem 3

Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

```{r}
One2Hundred <- c()
for (i in 1:100){
One2Hundred[i] <- i
}
One2seq <- seq(1,100)

print(One2Hundred)
print(One2seq)
```

### Problem 4

Find the sum of all the integer numbers from 1 to 100

With sum() function

```{r}
Summate <- sum(One2Hundred)
print(Summate)
```

With a loop

```{r}
SummateLoop <- 0L
for (i in 1:100) {
SummateLoop = SummateLoop + i
}

print(SummateLoop)
```

### Problem 5

Write a function to find the sum of all integers between any two values.

```{r}
SumAnyInterval <- function(IntStart,IntEnd){
  n <- 0
  for (i in IntStart:IntEnd){
    n = n+i
  }
  return(n)
}
```

Call the function:

```{r}
SumAnyInterval(5,200)
```

### Problem 6

List all of the odd numbers from 1 to 100.

Through the seq function:

```{r}
seq(1,100,by=2)
```

Through the use of mod and for loop

```{r}
Odds = c()
for (i in 1:100) {
  if (i%%2) {
    Odds = c(Odds,i)
  }
}
print(Odds)
```

### Problem 7
List all of the prime numbers from 1 to 1000.

```{r}
Primes <- c(2)
for (i in seq(3,1000,by=1)){
  test <- i%%Primes
  if (0%in%test){}else{
    Primes <- c(Primes,i)
  }
}
print(Primes)
```





### Problem 8
Generate 100 random numbers

```{r}
runif(100)
```


### Problem 9
Generate 100 random numbers within a specific range
```{r}
runif(100,2,5)
```


### Problem 10
Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: mean, mode, median, range, standard deviation

* It’s ok to use sum() and length()
* be creative and see if you can find multiple solutions.


```{r}
DescriptiveStats <- function(array){
  array2 = sort(array)
  len = length(array2)
  mean <- sum(array2)/len
  if (length(array2)%%2){
    median = array2[(len/2)+.5]
  }else{
    median = (array2[len/2] + array2[(len/2+1)])/2
  }
  current <- 0
  for (i in array2) {
    new <- length(which(array2==i))
    if (new>current) {
      current <- new
      mode <- array2[i]
    }
  }
  std <- sqrt(sum((array2 - mean)^2)/(len-1))
  
  return(c(mean,median,mode,std))
  
}

DescriptiveStats(c(1,2,3,4,5))
```

### Problem 11
Count the number of characters in a string variable

```{r}
String <- "Count the number of characters in this string"

CharSplit<- strsplit(String,"")
Count <- length(CharSplit[[1]])

print(Count)
```



### Problem 12
Count the number of words in a string variable


```{r}
String = "Count the number of words in this string"
WordSplit <- strsplit(String," ")

Count <- length(WordSplit[[1]])
print(Count)
```

### Problem 13

Count the number of sentences in a string variable.

```{r}
String = "Count the sentences in this String. Use the strsplit function."

SentenceSplit = strsplit(String,".",fixed=TRUE)
Count <- length(SentenceSplit[[1]])
print(Count)
```

Had to change the fixed option to TRUE. Most likely because of regex.


### Problem 14

Count the number of times a specific character occurs in a string variable

```{r}
CountAccurance <- function(char,string){
  split <- strsplit(string,"")
  split <- unlist(split)
  a <- data.frame(table(split))
  index <- which(a$split== char)
  return(a$Freq[index])
}

CountAccurance("c",String)
```

### Problem 15

Do a logical test to see if one word is found within the text of another string variable.
```{r}
TestWord <- "hello"
TestSentence <- "Is hello contained in this sentence?"

grepl(TestWord,TestSentence)
```

### Problem 16
Put the current computer time in milliseconds into a variable

```{r}

print(as.numeric(Sys.time())*1000, digits = 10)

```

### Problem 17

Measure how long a piece of code takes to run by measuring the time before the code is run, and after the code is run, and taking the difference to find the total time

```{r}
t1 = as.numeric(Sys.time())*1000
print(DescriptiveStats(c(Primes)))
t2 = as.numeric(Sys.time())*1000
print(t2-t1)
```

### Problem 18

Read a .txt file or .csv file into a variable

```{r}

# data = read.csv("track_points.csv")
```

### Problem 19

Output the contents of a variable to a .txt file

```{r}
# write.csv(data, file = "test.txt")
```

### Problem 20

Create a variable that stores a 20x20 matrix of random numbers


```{r}
m <- matrix(runif(25), nrow=5)
print(m)
```


### Problem 21
Output any matrix to a txt file using commas or tabs to separate column values, and new lines to separate row values


```{r}
# write.csv(m,"RandomMatrix.txt")
```

\newpage
## Harder Problems

### Problem 1
Fizzbuzz

```{r}

testvalues <- c(3,5)
outputstring <- c("Fizz","Buzz")
output = ""

for (i in 1:100) {


test <- !i%%testvalues

if (TRUE%in%test) {
output[i] <- paste(outputstring[test],collapse = "")
}else {
  output[i] <- as.character(i)
}
}
print(output)


```

other solution to fizzbuzz:

```{r}

fizzbuzz <- 1:100

mod3 <- !fizzbuzz%%3
mod5 <- !fizzbuzz%%5
mod35 <- mod3 & mod5
fizzbuzz[mod3] <- "Fizz"
fizzbuzz[mod5] <- "Buzz"
fizzbuzz[mod35] <- "FizzBuzz"

print(fizzbuzz)
```
Less code, but same test three times and harder to adapt new values or words.



### Problem 2

Frequency Counts
Take text as input, and be able to produce a table that shows the counts for each character in the text. This problem is related to the earlier easy problem asking you to count the number of times that a single letter appears in a text. The slightly harder problem is the more general version: count the frequencies of all unique characters in a text.


```{r}
testString <- "Many rabbits ran around the hollow hole"
```
```{r}

```

